If you see something, then say something to others: Complex contagions and the socially-contingent correction of misinformation

### 2018-03-26 manuscript_1.0.tex
draft update until simple misinformation exposure results

% declare documents and packages
\documentclass[man, 12pt, a4paper, nolmodern, noextraspace]{apa6}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{microtype}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{url}
\usepackage{times}
\renewcommand{\footnotesize}{\small} % use 11pt for footnotes
\usepackage[doublespacing]{setspace} % single space for footnotes
%\setlength{\skip\footins}{1.5pc plus 1pt} % some more space between footnote and main body
% this command put all footnotes to endnote at the end of the paper
\usepackage{endnotes}
\let\footnote\endnote

@@

\note{Word count: 5183 words \\ %\quickwordcount \\
    Draft date: \today \\
      \addvspace{.25in} 
      \textbf{Draft in progress. Please do not cite without permission.} \\
      Please direct any questions and inquiries to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}

@@

% Table 1.
\begin{table}[!htbp] \centering 
  \caption{\\ Descriptive Statistics of Cross-sectional Networks from Simulated Network Structures} 
  \label{tab:Table1} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \textbf{E-R} & \textbf{Chain} &  \textbf{SW No-Homophily} & \textbf{SW Homophily} \\ 
\hline \\[-1.8ex] 
Graph density & 0.000269 & 0.000268 & 0.000277 & 0.000272 \\ 
Mean degree & 1.292 & 1.287 & 1.327 & 1.303 \\ 
Max degree & 10.0 & 4.0 & 12.0 & 12.0 \\ 
Clustering coefficients & 0.0 & 0.0 & 0.02 & 0.01 \\ 
Mean distance & 2.2 & 2.2 & 4.5 & 3.4 \\ 
Homophilous ties & 49.4\% & 50.5\% & 52.3\% & 68.5\% \\ 
Heterophilous ties & 50.6\% & 49.5\% & 47.7\% & 31.5\% \\ 
\hline \\[-1.8ex]  
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\small \vspace{0.15in}
\textbf{Note:} E-R: Erdos Renyi random network. Chain: Chain network. SW No-Homophily: Small-world network absent of homophily. SW Homophily: Small-world network with partisan homophily. 
\end{tablenotes}
\end{table}

% Figure 1: Plots of static (cross-sectional) networks from simulations    
\begin{figure}
\captionsetup[figure]{labelfont={bf,it}}
\captionsetup[subfigure]{labelfont=bf,textfont=normalfont,singlelinecheck=on}
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots1.pdf} 
        \caption{Erdos-Renyi random network}
        \label{fig1:random}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots2.pdf} 
        \caption{Chain network} \label{fig1:tree}
    \end{subfigure}

    \vspace{1cm}
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots3.pdf} 
        \caption{Small-world network absent homophily} \label{fig1:nohomophily}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots4.pdf} 
        \caption{Baseline small-world network} \label{fig1:smallworld}
    \end{subfigure}

    \vspace{1cm}
    \captionsetup{format=hang}
    \caption{A cross-sectional view of simulated networks from different network topologies. Colored nodes represent nodes that have at least one connection with their neighbor (Red = Republicans, Blue = Democrats) while isolates at given time point was suppressed in visualization. A Erdos-Renyi (ER) random network (a) assumes a homogeneous probability of creating and dropping ties across all nodes conditional on observed density. A chain-like network (b) has more longer chains than the ER random network while lacks triangle-like structure due to constrains on degrees (less than three). While two small-world network has more star-like structure than others, our baseline small-world network (d) is more homophilous than competing specification in (c), as can be seen in Table \ref{tab:Table1}.} \label{fig:Figure1}
\end{figure}

  Adapting a well-known class of epidemic models, we simulated the dynamics of misinformation exposure and its correction on top of those stochastic network evolution models. We setup an environment consist of 2400 partisan actors (based on 2009 ANES panel survey's partisan composition: see footnote \ref{note6} for a detail) and simulate the diffusion dynamcics over 1000 simulated hours (roughly corresponds to 41 days) with 100 replicated simulations per each network topologies. We fit a series of SEIR (\enquote{suseptable - exposed - infected - recovered}) dynamic models for (a) a simple contagion of misinformation (i.e., a progression from \enquote{suspected} to \enquote{exposed}), (b) a progression from \enquote{exposed} to \enquote{infected} (i.e., those who believe a given misinformation conditional on exposure), and (c) a progression from \enquote{infected} to \enquote{recovered} conditional on exposure and adoption of corrective messages from their peers.

@@

    To date, how many times people exactly \enquote{share} fake news and misinformation on their social networks is not yet known to public. However, a recent study by \citeauthor{allcott2017social} (\citeyear{allcott2017social}) report that, for all 65 fake news websites they have identified during 2016 election, an individual visited such sites 0.64 times per month on average, and among them 41.8\% of all visits originate from social media traffics. Similarly, \citeauthor{guess2018selective} (\citeyear{guess2018selective}) report that of 27.4\% inidivduals who visited fake news websites, 22.1\% of all visites originate from social media.

  We start by setting our baseline prevalence, of which we arbitrary set 15\% of partisans are initially affected by misinformation and fake news. We then set our baseline \enquote{act rate} (i.e., the average number of transmissible acts per unit time per discussion tie) by taking the average of estimates from \citeauthor{allcott2017social} (\citeyear{allcott2017social}) and from \citeauthor{guess2018selective} (\citeyear{guess2018selective}), which yields 0.164 times per hour per discussion tie.\footnote{ \citeauthor{allcott2017social} report 0.64 $\times$ 41.8\% = 0.268 shares per unit time, while \citeauthor{guess2018selective} report 0.274 $\times$ 22.1\% = 0.060 shares per unit time. This averages to 0.164 times per unit time. We additionally assume all fake news website visits are driven by information sharing on social media.} We further assume 15\% of those who initially affected are only Republicans, given that the vast majority of identified fake news articles during 2016 U.S. presidential election were overwhelmingly pro-Trump \parencite[e.g.,][]{guess2018selective}. Here, we assume misinformation always flows from the \enquote{infected} (i.e., those who already believe given misinformation) to their suseptable peers (i.e., those who are not yet exposed to misinformation), but those who are being mere exposed do not contribute to misinformaiton flow (since the mere exposure does not necessarily mean they are endorsing such information) nor any other sources of exposure to misinformation is possible (i.e., partisan media exposure) for an individual to encounter such misinformation.

    Progression from \emph{being susceptible} (i.e., not yet being exposed) to \emph{being exposed} was determined by a simple contagion, such that a single contact with those who are infected ( = threshold of 1) is sufficient for partisans to be exposed to misinformation, yet conditional on the propensity for those who are infected to actually share such news (i.e., the probability of infection: see below). Following PEW data \parencite{pewfakenews} which suggests approximately 16\% of all partisans have had \emph{shared} fake news stories on their social network, we assume the risk of transmission of those who are already infected to share misinformation (i.e., infection probability per act) to be .16 in our simulations. Given those two parameters for the probability of infection per act (= .16) and the number of acts per unit time (= .164), the per-discussion tie transmission rate is calculated as an exponential function of the two, with a Bernoulli probability distribution controlling whether an infection event occurs. In addition, we additionally assume Republicans on average have a higher infection probability per act than Democrats -- once infected, Republicans are more likely to share such news than Democrats -- given the directional nature of misinformation being considered within this context (e.g., the vast majority of fake news articles during 2016 U.S. presidential election were overwhelmingly pro-Trump).

@@

\subsection{Corrective Message Exposure and a Recovery from Misperceptions}

%First, consistent with our prior discussion of simple vs. complex contagion dynamics, we assume that once exposed, individuals progress to \enquote{recovery} stage when a certain proportion (= $\rho$) of his or her neighbors are sending corrective messages debunking misinformation. We systematically vary the threshold value of $\rho$ to explore range of plausible values.

\section{Results}
\subsection{Simple Contagion of Misinformation Exposure}

>>>>

% declare documents and packages
\documentclass[man, 12pt, a4paper, nolmodern, noextraspace]{apa6}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{microtype}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{url}
\usepackage{times}
\usepackage{multirow} % multirow tables
\usepackage{arydshln} % dashline in tabular 
\renewcommand{\footnotesize}{\small} % use 11pt for footnotes
\usepackage[doublespacing]{setspace} % single space for footnotes
%\setlength{\skip\footins}{1.5pc plus 1pt} % some more space between footnote and main body
% this command put all footnotes to endnote at the end of the paper
\usepackage{endnotes}
\let\footnote\endnote

@@

\note{Word count: 6695 words \\ %\quickwordcount \\
    Draft date: \today \\
      \addvspace{.25in} 
      \textbf{Draft in progress. Please do not cite without permission.} \\
      Please direct any questions and inquiries to \href{mailto:hyunjin.song@univie.ac.at}{hyunjin.song@univie.ac.at}}

@@

% Table 1 and 2.
\begin{table}[!htbp] \centering 
	\begin{minipage}{\textwidth}
    \centering
  \caption{\\ Descriptive Statistics of Cross-sectional Networks from Simulated Network Structures} 
  \label{tab:Table1} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \textbf{E-R} & \textbf{Chain} &  \textbf{SW No-Homophily} & \textbf{SW Homophily} \\ 
\hline \\[-1.8ex] 
Graph density & 0.000269 & 0.000268 & 0.000277 & 0.000272 \\ 
Mean degree & 1.292 & 1.287 & 1.327 & 1.303 \\ 
Max degree & 10.0 & 4.0 & 12.0 & 12.0 \\ 
Clustering coefficients & 0.0 & 0.0 & 0.02 & 0.01 \\ 
Mean distance & 2.2 & 2.2 & 4.5 & 3.4 \\ 
Homophilous ties & 49.4\% & 50.5\% & 52.3\% & 68.5\% \\ 
Heterophilous ties & 50.6\% & 49.5\% & 47.7\% & 31.5\% \\ 
\hline \\[-1.8ex]  
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\small \vspace{0.15in}
\textbf{Note:} E-R: Erdos Renyi random network. Chain: Chain network. SW No-Homophily: Small-world network absent of homophily. SW Homophily: Small-world network with partisan homophily.\\ 
\end{tablenotes}
 	\end{minipage}
\bigbreak
\vspace{0.5in}
 	\begin{minipage}{\textwidth}
    \centering
\caption{\\ Misperception Recovery Scenarios by Network Topologies and Thresholds for Adopting Corrections} 
  \label{tab:Table2}

  \begin{tabular}{ ccccc}
\toprule
      \multicolumn{1}{c}{} &
      \multicolumn{1}{c}{Scenario I} &
      \multicolumn{3}{c}{Scenario II - Thresholds} \\
\cline{3-5}
 & \textbf{Asocial} & \textbf{0.25} & \textbf{0.5} & \textbf{0.75} \\
\hline \\[-1.8ex] 
              E-R & Model 1 & Model 2 & Model 3 & Model 4 \\ 
            Chain & Model 5 & Model 6 & Model 7 & Model 8 \\ 
  SW No-Homophily & Model 9 & Model 10 & Model 11 & Model 12 \\ 
  	 SW Homophily & Model 13 & Model 14 & Model 15 & Model 16 \\ 
\hline \\[-1.8ex]  
	\end{tabular}
 	\end{minipage}
\end{table}

% Figure 1: Plots of static (cross-sectional) networks from simulations    
\begin{figure}
\captionsetup[figure]{labelfont={bf,it}}
\captionsetup[subfigure]{labelfont=bf,textfont=normalfont,singlelinecheck=on}
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots1.pdf} 
        \caption*{A. Erdos-Renyi random network}
        \label{fig1:random}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots2.pdf} 
        \caption*{B. Chain network} \label{fig1:tree}
    \end{subfigure}

    \vspace{1cm}
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots3.pdf} 
        \caption*{C. Small-world network absent homophily} \label{fig1:nohomophily}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[trim={2cm 2cm 2cm 2cm}, clip, width=\linewidth]{draft/network_plots4.pdf} 
        \caption*{D. Baseline small-world network} \label{fig1:smallworld}
    \end{subfigure}

    \vspace{1cm}
    \captionsetup{format=hang}
    \caption{A cross-sectional view of simulated networks from different network topologies.} 
    \label{fig:Figure1}
    \captionsetup{font=small}
    \caption*{Note: Colored nodes represent nodes that have at least one connection with their neighbor (Red = Republicans, Blue = Democrats) while isolates at given time point was suppressed in visualization. A Erdos-Renyi (ER) random network ( = A) assumes a homogeneous probability of creating and dropping ties across all nodes conditional on observed density. A chain-like network ( = B) has more longer chains than the ER random network while lacks triangle-like structure due to constrains on degrees (less than three). While two small-world network has more star-like structure than others, our baseline small-world network (= D) is more homophilous than competing specification in its counterpart without homophily (= C), as can be seen in Table \ref{tab:Table1}.} 
\end{figure}

	Adapting a well-known class of epidemic models, we simulated the dynamics of misinformation exposure and its correction on top of those stochastic network evolution models. We setup an environment consist of 2400 partisan actors (based on 2009 ANES panel survey's partisan composition: see footnote \ref{note6} for a detail) and simulate the diffusion dynamics over 1000 simulated hours (roughly corresponds to 41 days) with 100 replicated simulations per each network topologies. We fit a series of SEIR (\enquote{susceptible - exposed - infected - recovered}) dynamic models for (a) a simple contagion of misinformation (i.e., a progression from \enquote{suspected} to \enquote{exposed}), (b) a progression from \enquote{exposed} to \enquote{infected} (i.e., those who believe a given misinformation conditional on exposure), and (c) a progression from \enquote{infected} to \enquote{recovered} conditional on exposure and adoption of corrective messages from their peers.

@@

    To date, how many times people exactly \enquote{share} fake news and misinformation on their social networks is not yet known to public. However, a recent study by \citeauthor{allcott2017social} (\citeyear{allcott2017social}) report that, for all 65 fake news websites they have identified during 2016 election, an individual visited such sites 0.64 times per month on average, and among them 41.8\% of all visits originate from social media traffics. Similarly, \citeauthor{guess2018selective} (\citeyear{guess2018selective}) report that of 27.4\% individuals who visited fake news websites, 22.1\% of all visits originate from social media.

	We start by setting our baseline prevalence, of which we arbitrary set 15\% of partisans are initially affected by misinformation and fake news. We then set our baseline \enquote{act rate} (i.e., the average number of transmissible acts per unit time per discussion tie) by taking the average of estimates from \citeauthor{allcott2017social} (\citeyear{allcott2017social}) and from \citeauthor{guess2018selective} (\citeyear{guess2018selective}), which yields 0.164 times per hour per discussion tie.\footnote{ \citeauthor{allcott2017social} report 0.64 $\times$ 41.8\% = 0.268 shares per unit time, while \citeauthor{guess2018selective} report 0.274 $\times$ 22.1\% = 0.060 shares per unit time. This averages to 0.164 times per unit time. We additionally assume all fake news website visits are driven by information sharing on social media.} We further assume 15\% of those who initially affected are only Republicans, given that the vast majority of identified fake news articles during 2016 U.S. presidential election were overwhelmingly pro-Trump \parencite[e.g.,][]{guess2018selective}. Here, we assume misinformation always flows from the \enquote{infected} (i.e., those who already believe given misinformation) to their susceptible peers (i.e., those who are not yet exposed to misinformation), but those who are being mere exposed do not contribute to misinformation flow (since the mere exposure does not necessarily mean they are endorsing such information) nor any other sources of exposure to misinformation is possible (i.e., partisan media exposure) for an individual to encounter such misinformation.

    Progression from \emph{being susceptible} (i.e., not yet being exposed) to \emph{being exposed} was determined by a simple contagion, such that a single contact with those who are infected ( = threshold of 1) is sufficient for partisans to be exposed to misinformation, yet conditional on the propensity for those who are infected to actually share such news (i.e., the probability of infection: see below). Following PEW data \parencite{pewfakenews} which suggests approximately 16\% of all partisans have had \emph{shared} fake news stories on their social network, we assume the risk of transmission of those who are already infected to share misinformation (i.e., infection probability per act) to be .16 in our simulations. Given those two parameters for the probability of infection per act (= .16) and the number of acts per unit time (= .164), the per-discussion tie transmission rate is calculated as an exponential function of the two, with a Bernoulli probability distribution controlling whether an infection event occurs. In addition, we additionally assume Republicans on average have a higher infection probability per act than Democrats (=.04 higher than Democrats) -- once infected, Republicans are more likely to share such news than Democrats -- given the directional nature of misinformation being considered within this context (e.g., the vast majority of fake news articles during 2016 U.S. presidential election were overwhelmingly pro-Trump).

@@

\subsection{Corrective Message Exposure and a Recovery from Misperceptions}
	For corrective message exposure and subsequent progression from \emph{being infected} to \emph{being recovered}, we examine two possible scenarios -- the first model closely approximate a single-shot, \emph{asocial} correction, in that the model assumes  corrections are randomly received for infected individuals, following individual-level stochastic process of adopting such corrections given exposure. This model therefore assumes no social-dynamics surrounding the misinformation correction, as typically assumed in extant experimental literature. Our second, more realistic model is more consistent with our prior discussion of simple vs. complex contagion dynamics, in that once exposed, individuals progress to recovery state when a certain proportion (= $\rho$) of his or her neighbors are sending corrective messages that debunking misinformation. We systematically vary the threshold value of $\rho$ to explore system-level consequences of social dynamics surrounding misinformation corrections. Below Table \ref{tab:Table2} lists all scenarios for the combination of network topological structure and the threshold value of $\rho$ in misperception recovery.

\section{Results}
\subsection{Simple Contagion of Misinformation Exposure}
	We first look at the simple contagion dynamics of misinformation exposure (assuming no recovery by corrections throughout the simulated time periods) and propagation rates across different network typologies over time, as depicted in Figure \ref{fig:Figure2} and in Table \ref{tab:Table3} below. The results reveal that network structures have somewhat non-trivial effects on the dynamics of misinformation propagation at population level. It seems that our baseline network model (i.e., small-world network with partisan homophily) appears to be bit better in terms of disseminating given misinformation more faster than other network structures -- that is, we do find some modest evidence that spread of simple misinformation spreads faster in our small world networks (red lines in Panel A of Figure \ref{fig:Figure2}) than in random networks (black lines in Panel A of Figure \ref{fig:Figure2}) when misinformation is spread via simple contagion (i.e., a single contact with those who are infected) followed by a individual-level stochastic progression to being infected given exposure to misinformation.

    Although differences among the cumulative exposure fractions in different network structures were not appear to be vastly different from each other (as their confidence intervals of cumulative exposure fractions significantly overlap with each other: see online supplementary materials for a detail), their exposure rates (as measured by the number of newly exposed individuals at given time point) do differ with each other as can be seen in Figure \ref{fig:Figure2} below. This was especially true between our baseline network (red lines) and random networks (black lines) as indicated in Table \ref{tab:Table4}. We used the Wilcoxon Rank Sum Test (a nonparametric test of differences of two population distributions) to test whether the two proportions of newly exposed to misinformation among the susceptible (= no. of SI flow divided by no. of susceptible per each time point) significantly differ from each other between different network topologies. The cell entries of Table \ref{tab:Table4} refer to the range of simulated time points in which two distributions of adoption rates statistically different from each other based on Wilcoxon Rank Sum Test. For instance, Table \ref{tab:Table4} indicates that from 58 to 901 time points, the distribution of the fraction of newly exposed to misinformation from ER random network and that from our baseline small-world homophily network statistically different from zero (less than .05). The results shows that across range of time points excluding the very initial stage of misinformation propagation, network structure induces statistically different adoption rates over time.

\begin{figure}
\captionsetup[figure]{labelfont={bf,it}}
    \centering

    \begin{subfigure}[t]{0.8\textwidth}
        \centering
        \includegraphics[clip, width=\linewidth, page = 1]{draft/Figure_2__Prevalence.pdf} 
        \captionsetup{font=small}
        \caption*{Panel A. Overall Cumulative Prevalence of Misinformation.}
    \end{subfigure}

    \begin{subfigure}[t]{0.8\textwidth}
        \centering
        \includegraphics[clip, width=\linewidth, page = 2]{draft/Figure_2__Prevalence.pdf} 
        \captionsetup{font=small}
        \caption*{Panel B. Susceptible - Exposed Flow, measured as the number of newly exposed to misinformation}
    \end{subfigure}

    \captionsetup{format=hang}
    \caption{Prevalence and Exposed - Infected Flow of Misinformation Over Time (Assuming No Recoveries) by Network Topologies, Averaged Over 100 Simulations.} 
    \label{fig:Figure2}
    \captionsetup{font=small}
    \caption*{Note: Straight lines in Panel A represent fraction of those who are being exposed to misinformation, whereas dotted lines represent fraction of those who are susceptible. X-axis represents simulated times (in hours) and Y-axis represents the fraction exposed to misinformation (in panel A) or rates of misinformation exposure (in panel B). Black = Erdos-Renyi random network, Grey = Chain network, Blue = Small-world absent homophily, and Red = baseline small-world homophily network.} 
\end{figure}

\begin{table}[!htbp] 
	\begin{minipage}{\textwidth}
    \centering
  \caption{\\ Overall Prevalence of Misinformation Over Time by Network Topologies (Cumulative Exposure, No Recovery Scenarios)} 
  \label{tab:Table3} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \textbf{E-R} & \textbf{Chain} & \textbf{SW No-Homophily} & \textbf{SW Homophily} \\ 
\hline \\[-1.8ex] 
\textbf{Overall} & .594 & .584 & .605 & .640 \\ 
(95\% CIs) & [.564, .624] & [.558, .609] & [.574, .635] & [.608, .669] \\ 
\hdashline
\textbf{Among Dem} & .295 & .290 & .301 & .312 \\ 
(95\% CIs) & [.274, .316] & [.271, .308] & [.279, .322] & [.287, .332] \\ 
\hdashline
\textbf{Among Rep} & .299 & .295 & .305 & .330 \\ 
(95\% CIs) & [.285, .313] & [.282, .307] & [.290, .319] & [.315, .343] \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\small \vspace{0.15in}
\textbf{Note:} E-R: Erdos Renyi random network. Chain: Chain network. SW No-Homophily: Small-world network absent of homophily. SW Homophily: Small-world network with partisan homophily. All statistics are based on 100 random simulations over 1000 time points from the same setup per network topologies. \\ 
\end{tablenotes}
\end{minipage}
\bigbreak
\vspace{0.5in}
 	\begin{minipage}{\textwidth}
    \centering
  \caption{\\Time Durations Within Which WRS Test of Differences on Fraction of Newly Exposed of Misinformation Over Time are Significantly Different From Each Other Across Topologies} 
  \label{tab:Table4} 
  \begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \textbf{E-R} & \textbf{Chain} & \textbf{SW No-Homophily} & \textbf{SW Homophily} \\ 
\hline \\[-1.8ex] 
\textbf{Chain} & 106 : 278 & - &  &  \\ 
\textbf{SW No-Homophily} &  68 : 1000 &  70 : 585 & - &  \\ 
\textbf{SW Homophily} &  58 : 901 &  63 : 942 & 151 : 1000 & - \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}[para,flushleft]
\small \vspace{0.15in}
\textbf{Note:} E-R: Erdos Renyi random network. Chain: Chain network. SW No-Homophily: Small-world network absent of homophily. SW Homophily: Small-world network with partisan homophily. Cell entries denote the range of time points in which Wilcoxon Rank Sum test indicates the adoption rates from two network topologies statistically different from each other (p < 0.05). \\ 
\end{tablenotes}
\end{minipage}
\end{table}
